Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/desiderata.tex

Critically, all three desiderata are trivial to satisfy on their own. Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action). Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP. Now consider \textsc{Optimality}. Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$. Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.

The interesting (and difficult) case is satisfying {\it both} desiderata. To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

>>>>

Critically, all three desiderata are trivial to satisfy on their own. Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action). Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP. Now consider \textsc{Optimality}. Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$. Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}. Lastly for \textsc{Efficient-Computability}, returning an MDP $M_A$, such that $M_A$ is identical to $M_G$ is trivially efficiently computable.

The interesting (and difficult) case is satisfying {\it all three} desiderata. To the best of our knowledge, no abstraction has been formally proven to satisfy all three. In the next section, we discuss prior methods of abstraction, and their statuses relative to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.
